\documentclass{amsart}
% For maths symbols, and theorem's etc
\usepackage{amsmath, amsthm}

\theoremstyle{definition}
\newtheorem{class}{Class}

\theoremstyle{remark}
\newtheorem{rmk}{Remark}

\newcommand{\mcC}{\mathcal{C}}

\title{Recursive strategies}

\begin{document}

\maketitle

Given a permutation class $\mcC$ a \emph{proof strategy} for a tiling $T$
returns a disjoint set of tilings $T_1, T_2, \ldots, T_k$ such that the union of
these individually intersected with $\mcC$ is the tiling $T$, i.e.
\[
  T \cap \mcC = ( T_1 \cap \mcC ) \sqcup ( T_2 \cap \mcC ) \sqcup \cdots \sqcup (T_k \cap \mcC).
\]
If the proof strategy returns a single tiling we call it an \emph{equivalence}
proof strategy. If returns more than one we call it a \emph{batch} proof
strategy.

For a permutation class $\mcC$, consider the tree where the root node is the $1
\times 1$ tiling with $\mcC$. The \emph{children} of a node are the tilings
obtained by a proof strategy on it, thus form a disjoint union for the node
while working inside $\mcC$. If all the leaves of the tree are subsets of $\mcC$
then they define a cover for $\mcC$, while the tree itself is a proof
certificate of this cover. We call such trees \emph{proof trees}.

Here is a rough outline of how we propose to search for proof trees.

\begin{rmk}[Outline of basic proof tree search]
  In order to find a cover for $\mcC$ we create an and-or tree. The root node is
  the $1 \times 1$ tiling with $\mcC$ and originally set to \textsf{False}, as
  we reject the trivial cover. For a node with tiling $T$, and for each proof
  strategy we add to his children the tilings from the proof strategy and
  conjoin the edges to these. When a tiling is a subset of $\mcC$, it is marked
  as \textsf{True} and this information is propagated through the tree. When
  edges are conjoined, this represents an ``and'', therefore in order for a node
  to be \textsf{True} then a set of its children which are conjoined must all be
  \textsf{True}. The ``or'' part of the tree is that we need only one set of
  conjoined children to be \textsf{True}. When the root node becomes
  \textsf{True} then we know that the search tree contains a proof tree for
  $\mcC$.
\end{rmk}

We will do this in the following way, we will create OrNodes, which will consist
of single tilings. From a tiling/OrNode, first we create the SiblingNode, which
will consist of all tilings reachable by equivalent proof strategies, we call
these \emph{sibling} tilings. In order for the SiblingNode to be verified we
require that one of the sibling tilings to be verified.

For each batch strategy we create an AndNode which will consist of the set of
OrNodes with tilings corresponding to the strategy. In order for an AndNode to
be verified, all of the OrNodes in its set must be verified.

The remainder of this document will discuss recursive strategies, in an informal
way. (For want of a better name) A \emph{recursive} strategy (these don't fit
the definition of strategies given above) for a tiling, is a set of subtilings
(currently disjoint), that if the enumeration/permutations are known for, then
the enumeration/permutations are known for the tiling. There are three ways for
a subtiling to be verified
\begin{itemize}
  \item it is verified as subset of $\mcC$,
  \item it points to a verified node elsewhere in the tree,
  \item or it points to an ancestor of the tiling.
\end{itemize}

Here is how we propose to find such proof trees relying on recursive strategies
while maintaining the original proof trees definition. We will still use the
OrNodes, AndNodes and SiblingNodes described above, but now keep track of
more information.

\begin{class}[OrNode]
  \leavevmode
  \begin{itemize}
    \item a tiling $T$,
    \item a SiblingNode - we will discuss this more when introducing
    SiblingNodes, but essentially it stores reachable siblings of $T$,
    \item the set of ancestral OrNodes,
    \item parent AndNodes - (the strategies it belong too),
    \item children AndNodes - (the batch strategies from an $T$).
  \end{itemize}
\end{class}

We realized while trying to propagate ancestral verification the lack of
knowledge of ancestors made things complicated. Therefore as you can see we have
adopted the approach of storing ancestral OrNodes as we go.

Note since we are storing the ancestral OrNodes, a tiling $T$ will belong to
multiple OrNodes. However, the work done a tiling $T$ will only ever be done
once and stored in the cache.

\begin{class}[AndNode]
\leavevmode
\begin{itemize}
  \item a parent OrNode with tiling $T$,
  \item a set of OrNodes corresponding to a batch strategy on $T$,
  \item formal step explaining the corresponding batch strategy
  \item a set of ancestral OrNodes.
\end{itemize}
\end{class}

\begin{class}[SiblingNode]
  \leavevmode
\begin{itemize}
  \item a set of OrNodes with equivalent tilings,
  \item a map explaining the equivalences,
  \item a set of ancestral OrNodes.
\end{itemize}
\end{class}

Let's discuss what we do when we expand the search tree. We first find an
unverified OrNode $x$ with tiling $T$ to be expanded. For each batch strategy
from the tiling $T$, we create an OrNode with each of the strategy's tilings and
then an AndNode with them all.

When we create the OrNode for a tiling $T$, we also create a SiblingNode with
each of the equivalent proof strategies on the tiling $T$.

Now, consider a recursive strategies $S$ for $T$ in OrNode $x$. For each $T'$ in
$S$ if the tiling is not in the cache we create the OrNode but do not expand it
until it is found naturally. If it is in the cache and one of its OrNodes is
verified, it is verified. If it is verified by the verification check, it is
verified. The final case is if it points somewhere unverified, say node $y$. We
make a new OrNode with $T'$ if and only if $y$ is in the ancestral set of node
$x$, and mark it verified. All of the tiling's OrNodes in $S$ are then connected
together in an AndNode. We can propagate verified in the normal way.

Note, we believe this removes the need for different types of verified. The
challenge then comes from keeping track of ancestral nodes, and for combining
siblings in SiblingNodes.





\end{document}
